---
title: "Assignment-B1"
output: github_document
date: "2024-10-29"
---
### Load Libraries
```{r,message = FALSE}
library(tidyr)
library(ggplot2)
library(dplyr)
library(datateachr)
library(palmerpenguins)
library(testthat)
```
## Exercise 1 & 2
From the mda project, I made some plots depending on the types of the independent and dependent variables. Every time I need to rewrite the ggplot function to get the plots, so I create this function in order to reduce repeating work for plotting. 

To be specific, if I want to see the distribution of two numeric variables, I can just input the names of two numeric variables as arguments to get a scatter plot from my function. While, if I want to check the relationship between a categorical independent variable and a numeric dependent variable, I can input the names of the categorical variable and the numeric variable as arguments to get a jitter plot from my function. 

**Notice:** 

- This function only works in **two situations**:
  - the two variables are both numeric 
  - the independent variable is categorical and the dependent variable is numeric.
  
- Before generating plots, **the missing values in the variables will be removed**. For example, a 'NA' category isn't included in the jitter plot.
```{r}
#' @title my_plot
#' @description This function produces jitter plots for categorical independent variables & numeric dependent variables, and scatter plots for numeric independent & dependent variables.
#' @param data The dataset we will use, which can be data.frame or tibble. The naming is straightforward.
#' @param independent_var The independent variable, which can be categorical or numeric. The naming is straightforward.
#' @param dependent_var The dependent variable, which can only be numeric. The naming is straightforward.
#' @param a The alpha transparency that can be customized. Naming it after the initial of "alpha".
#' @return A plot (ggplot object) reflecting the relationship or distirbution between the two variables, it can be jitter plot or scatter plot.
my_plot <- function(data, independent_var, dependent_var, a) {
  # Check dataset form
  if (!is.data.frame(data)) {
    stop("data should be a data.frame or a tibble")
  }
  # Check the existence of independent variable
  if (!(independent_var %in% names(data))) {
    stop(paste("independent variable", independent_var, "is not in the dataset"))
  }
  # Check the existence of dependent variable
  if (!(dependent_var %in% names(data))) {
    stop(paste("dependent variable", dependent_var, "is not in the dataset"))
  }
  # Remove missing values
  plot_data <- data %>%
    select(all_of(c(independent_var, dependent_var))) %>%
    drop_na()
  # Check whether dependent variable is numeric
  if (!is.numeric(plot_data[[dependent_var]])) {
    stop("dependent variable is not numeric")
  }
  # For categorical independent variables
  if (is.character(plot_data[[independent_var]]) || is.factor(plot_data[[independent_var]])) {
    # Jitter plot for categorical and numeric
    p <- ggplot(plot_data, aes(x = .data[[independent_var]], y = .data[[dependent_var]])) +
      geom_jitter(alpha = a) +
      labs(
        title = paste("Distribution of", dependent_var, "by", independent_var),
        x = independent_var,
        y = dependent_var
      ) +
      theme_minimal()
  }
  # For numeric independent variables
  else if (is.numeric(plot_data[[independent_var]])) {
    # Scatter plot for both numeric
    p <- ggplot(plot_data, aes(x = .data[[independent_var]], y = .data[[dependent_var]])) +
      geom_point(alpha = a) +
      labs(
        title = paste("Relationship between", independent_var, "and", dependent_var),
        x = independent_var,
        y = dependent_var
      ) +
      theme_minimal()
  } else {
    stop("this function only accpets：
1. independent variable is categorical and dependent variable is numeric
2. both variables are numeric")
  }
  return(p)
}
```

## Exercise 3
### Example 1: Both variables are numeric
The data used here is the "penguins" dataset from "palmerpenguins".
First, have a look at the content of the dataset.
```{r}
print(penguins)
```
Choose the numeric independent variable "bill_length_mm" and the numeric dependent variable "body_mass_g", then draw a scatter plot for them.
```{r}
my_plot(penguins,"bill_length_mm", "body_mass_g",0.5)
```

### Example 2: Independent variables are categorical while dependent variables are numeric
The data used here is the "apt_buildings" dataset from "datateachr".
First, have a look at the content of the dataset.
```{r}
print(apt_buildings)
```
Choose the categorical independent variable "visitor_parking" and the numeric dependent variable "no_of_accessible_parking_spaces", then draw a jitter plot for them.
```{r}
my_plot(apt_buildings,"visitor_parking", "no_of_accessible_parking_spaces", 0.3)
```


### Exercise 4
What I want to test is about the input of the function and the properties of the output plots.

#### Test 1: Check the return type of the function
```{r}
test_that("Function returns ggplot object",{
  generated_plot <- my_plot(penguins, "species", "flipper_length_mm",0.5)
  expect_is(generated_plot,"ggplot")
})
```

#### Test 2: Check the existance of input variables
```{r}
test_that("The input variable doesn't exist in the dataset",{
  expect_error( my_plot(penguins, "abc", "flipper_length_mm",0.5),"independent variable abc is not in the dataset")
})
```

#### Test 3: Check the class of input variables
```{r}
test_that("The type of input variable is not accepted",{
  expect_error( my_plot(apt_buildings, "no_of_units", "window_type",0.5),"dependent variable is not numeric")
})
```

#### Test 4: Check if the missing values in variables are removed before plotting
```{r}
test_that("The missing values are removed",{
  generated_plot <- my_plot(penguins, "species", "flipper_length_mm", 0.5)
  expected_data <- penguins %>%
    select(species, flipper_length_mm) %>%
    drop_na()
  expect_equal(generated_plot$data, expected_data)
})
```

#### Test 5: Check the properties of the layers of the plot
```{r}
test_that("The plot has only one layer and the layer uses point geometry",{
  generated_plot <- my_plot(penguins, "island", "body_mass_g", 0.5)
  expect_equal(length(generated_plot$layers), 1)
  expect_true(inherits(generated_plot$layers[[1]]$geom, "GeomPoint"))
})
```

#### Test 6: Check if the alpha transparency of the plot is euqal to the input argument 'a'
```{r}
test_that("The transparency is equal",{
  generated_plot <- my_plot(penguins, "species", "body_mass_g", 0.7)
  expect_equal(generated_plot$layers[[1]]$aes_params$alpha, 0.7)
})
```